#exercise 4
*1.Load the Boston data from the MASS package.*
```{r}
library(MASS)
data("Boston")
str(Boston)
summary(Boston)
```
  
  There are 506 observations and 14 variables in the Boston data. The details about the meanings of 14 varibles are here,you can learn from this through this link https://stat.ethz.ch/R-manual/R-devel/library/MASS/html/Boston.html  
*2.Show a graphical overview of the data and show summaries of the variables in the data.*  

```{r}
library(corrplot)
library(MASS)
library(dplyr)
 cor_matrix<-cor(Boston) %>% round(digits = 2)
 cor_matrix
```
  
Then we can visualize the correlation matrix
```{r}
corrplot(cor_matrix, method="circle", type="upper", cl.pos="b", tl.pos="d", tl.cex = 0.6)
```
  
  
*3.Standardize the dataset and print out summaries of the scaled data*
```{r}
boston_scaled <- scale(Boston)
summary(boston_scaled)
class(boston_scaled)
boston_scaled <- as.data.frame(boston_scaled)
```

Use the quantiles as the break points in the categorical variable. Drop the old crime rate variable from the dataset. Divide the dataset to train and test sets, so that 80% of the data belongs to the train set. 
```{r}

bins <- quantile(boston_scaled$crim)
bins
string <-c("low","med_low","med_high","high")
string
crime <- cut(boston_scaled$crim, breaks = bins, include.lowest = TRUE,label=string)
table(crime)
boston_scaled <- dplyr::select(boston_scaled, -crim)
n <- nrow(boston_scaled)
ind <- sample(n,  size = n * 0.8)
train <- boston_scaled[ind,]
test <- boston_scaled[-ind,]
correct_classes <- test$crime


```

*4Fit the linear discriminant analysis on the train set. Use the categorical crime rate as the target variable and all the other variables in the dataset as predictor variables. Draw the LDA (bi)plot*
```{r}

```