---
title: "chapter 5.rmd"
author: "Xiaodan Ouyang"
date: "2020/11/26"
output: html_document
---
*1.Show a graphical overview of the data and show summaries of the variables in the data.*
```{r}
human<-read.csv(file = "data/human.csv")
ggpairs(human,cardinality_threshold=155)

```

*2.Perform principal component analysis (PCA) on the not standardized human data. Show the variability captured by the principal components. Draw a biplot displaying the observations by the first two principal components (PC1 coordinate in x-axis, PC2 coordinate in y-axis)* 


```{r}
str(human)
human$GNI <- as.numeric(as.character(human$GNI))
human$Mat.Mor<- as.numeric(as.character(human$Mat.Mor))
cor(human) %>% corrplot
human_std <- scale(human)
summary(human_std)
pca_human <- prcomp(human_std)
biplot(pca_human, choices = 1:2,cex = c(0.8, 1),col = c("grey40", "deeppink2"))
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
